\documentclass[11pt, conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphics, wrapfig}
\usepackage{courier}
\usepackage{url, hyperref}

\title{ECE 509 Project Outline}
\author{Cody Gunton and Joshua Mack}
\date{30 March, 2017}

\begin{document}

\maketitle
\section{Introduction}
\begin{itemize}
    \item Briefly set up the problem we are interested in, the techniques that will be used, summarize related work, and outline our conclusions.
\end{itemize}

\section{Background on Convolutional Neural Networks}
\begin{itemize}
    \item Brief overview of standard neural networks
    \item Changes made from standard neural networks to convolutional networks and the advantages they provide in this context.
\end{itemize}

\section{Background on Cryptography and Cryptanalytic Techniques}
\begin{itemize}
    \item Alice, Bob and Eve; symmetric vs asymmetric; simple ciphers we will look for.
    \item Cryptanalytic techniques: frequency analysis and its variants; known plain/ciphertext; differential analysis.
\end{itemize}

\section{Implementation Details}
\begin{itemize}
    \item Basic concepts of TensorFlow
    \item Description of our networks
    \item Details of training 
\end{itemize}

\section{Cryptanalysis}
\begin{itemize}
    \item For some of the aforementioned cryptanalysis techniques, provide our attempt to attack the networks' cryptography by that method.
    \item Discuss how to train to avoid these techniques of cryptanalysis. 
\end{itemize}

\section{Possible Applications} 
\begin{itemize}
    \item Training what to protect?
    \item Censoring/redaction applications?
\end{itemize}
\section{Conclusion and Further Questions}
\begin{itemize}
    \item Summarize conclusions.
    \item Discuss issues surrounding training nets to use asymmetric ciphers?
    \item Possible adjustments to network setup and training techniques?
\end{itemize}
\section{Appendix: Code}

\begin{thebibliography}{9}
\bibitem{Example} 
Gauss, Cark Friedrich, \textit{disquisitiones arithmeticae}, Scroll of paper, 1789.


\end{thebibliography}
\end{document}
